---
title: "Harry Potter"
author: "Prathyusha"
date: "August 12, 2017"
output: html_document
---

```{r}

if (packageVersion("devtools") < 1.6) {
  install.packages("devtools")
}

devtools::install_github("bradleyboehmke/harrypotter")

```
```{r}
#install.packages("tidyverse", dependencies = TRUE)
library(tidyverse)      # data manipulation & plotting
library(stringr)        # text cleaning and regular expressions
library(tidytext)       # provides additional text mining functions
library(harrypotter)    # provides the first seven novels of the Harry Potter series
# we need to install psych package inorder to work on tidyverse and tidytext



```


```{r}
sentiments

```


AFINN -from Finn Årup Nielsen ( lexicon assigns words with a score that runs between -5 and 5, with negative scores indicating negative sentiment and positive scores indicating positive sentiment)
bing - from Bing Liu and collaborators (lexicon categorizes words in a binary fashion into positive and negative categories)
nrc - from Saif Mohammad and Peter Turney (lexicon categorizes words in a binary fashion (“yes”/“no”) into categories of positive, negative, anger, anticipation, disgust, fear, joy, sadness, surprise, and trust)

```{r}
# to see the individual lexicons try
get_sentiments("afinn")
get_sentiments("bing")
get_sentiments("nrc")



```

```{r}
#Basic sentiment analysis
titles <- c("Philosopher's Stone", "Chamber of Secrets", "Prisoner of Azkaban",
            "Goblet of Fire", "Order of the Phoenix", "Half-Blood Prince",
            "Deathly Hallows")

books <- list(philosophers_stone, chamber_of_secrets, prisoner_of_azkaban,
           goblet_of_fire, order_of_the_phoenix, half_blood_prince,
           deathly_hallows)
  
series <- tibble()

for(i in seq_along(titles)) {
        
        clean <- tibble(chapter = seq_along(books[[i]]),
                        text = books[[i]]) %>%
             unnest_tokens(word, text) %>%
             mutate(book = titles[i]) %>%
             select(book, everything())

        series <- rbind(series, clean)
}

```


```{r}
# set factor to keep books in order of publication
series$book <- factor(series$book, levels = rev(titles))

series

```


```{r}
# To check nrc sentiment values
series %>%
        right_join(get_sentiments("nrc")) %>%
        filter(!is.na(sentiment)) %>%
        count(sentiment, sort = TRUE)
```


```{r}
# To check the sentiment change over the course of each novel
series %>%
        group_by(book) %>% 
        mutate(word_count = 1:n(),
               index = word_count %/% 500 + 1) %>% 
        inner_join(get_sentiments("bing")) %>%
        count(book, index = index , sentiment) %>%
        ungroup() %>%
        spread(sentiment, n, fill = 0) %>%
        mutate(sentiment = positive - negative,
               book = factor(book, levels = titles)) %>%
        ggplot(aes(index, sentiment, fill = book)) +
          geom_bar(alpha = 0.5, stat = "identity", show.legend = FALSE) +
          facet_wrap(~ book, ncol = 2, scales = "free_x")

````


```{r}
# comparing sentiments

afinn <- series %>%
        group_by(book) %>% 
        mutate(word_count = 1:n(),
               index = word_count %/% 500 + 1) %>% 
        inner_join(get_sentiments("afinn")) %>%
        group_by(book, index) %>%
        summarise(sentiment = sum(score)) %>%
        mutate(method = "AFINN")

bing_and_nrc <- bind_rows(series %>%
                  group_by(book) %>% 
                  mutate(word_count = 1:n(),
                         index = word_count %/% 500 + 1) %>% 
                  inner_join(get_sentiments("bing")) %>%
                  mutate(method = "Bing"),
          series %>%
                  group_by(book) %>% 
                  mutate(word_count = 1:n(),
                         index = word_count %/% 500 + 1) %>%
                  inner_join(get_sentiments("nrc") %>%
                                     filter(sentiment %in% c("positive", "negative"))) %>%
                  mutate(method = "NRC")) %>%
        count(book, method, index = index , sentiment) %>%
        ungroup() %>%
        spread(sentiment, n, fill = 0) %>%
        mutate(sentiment = positive - negative) %>%
        select(book, index, method, sentiment)
        
```


```{r}
# To bind and plot

bind_rows(afinn, 
          bing_and_nrc) %>%
        ungroup() %>%
        mutate(book = factor(book, levels = titles)) %>%
  ggplot(aes(index, sentiment, fill = method)) +
  geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
  facet_grid(book ~ method)
````

```{r}
#common sentiment words

bing_word_counts <- series %>%
  inner_join(get_sentiments("bing")) %>%
  count(word, sentiment, sort = TRUE) %>%
  ungroup()

bing_word_counts
````

```{r}
# Top n words for each setiment 
bing_word_counts %>%
        group_by(sentiment) %>%
        top_n(10) %>%
        ggplot(aes(reorder(word, n), n, fill = sentiment)) +
          geom_bar(alpha = 0.8, stat = "identity", show.legend = FALSE) +
          facet_wrap(~sentiment, scales = "free_y") +
          labs(y = "Contribution to sentiment", x = NULL) +
          coord_flip()
```


```{r}
# sentiment Analysis with large units

````